Inference methods comparison for the simplified Naomi model

### 2023-02-09 src/naomi-simple_compare/comparison.Rmd
Update comparison, and split beta parameters which are really multiple up in histogram_and_ecdf() #20

We compare the inference results from `TMB`, `aghq` and `tmbstan`.
Import these inference results as follows:

@@

## `beta`

```{r}
lapply(pars[stringr::str_starts(pars, "beta")], histogram_and_ecdf)
```

@@

```{r}
histogram_and_ecdf_helper <- function(par) lapply(1:sum(names(tmb$fit$obj$env$par) == par), histogram_and_ecdf, par = par)
histogram_and_ecdf_helper("u_rho_x")
```

>>>>

We compare the inference results from `TMB`, `aghq`, `adam`, and `tmbstan`.
Import these inference results as follows:

@@

## `beta_rho`

```{r}
histogram_and_ecdf_helper <- function(par) lapply(1:sum(names(tmb$fit$obj$env$par) == par), histogram_and_ecdf, par = par)
histogram_and_ecdf_helper("beta_rho")
```

## `beta_alpha`

```{r}
histogram_and_ecdf_helper("beta_alpha")
```

## `beta_lambda`

```{r}
histogram_and_ecdf_helper("beta_lambda")
```

## `beta_anc_rho`

```{r}
histogram_and_ecdf("beta_anc_rho")
```

## `beta_anc_alpha`

```{r}
histogram_and_ecdf("beta_anc_alpha")
```

@@
